Spin canonical divisors of log stacky curves

### 2015-07-02 stacky_write_up/spin_cring.tex
editing moster proof

The main theorem of this paper, Theorem ~\ref{thm:main}, combined
with a lemma of Voight and Zureick-Brown \cite[Lemma 10.2.1]
{vzb:stacky}, provides a statement on rings of modular forms.
Together with the main theorem from Voight and Zureick-Brown \cite
[Theorem 9.3.1]{vzb:stacky}, we have the following application to
rings of modular forms. Note that the lemma from Voight and Zureick-
Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately
from the classical work of Kodaira--Spencer
\cite{kodaira-spencer:deformations}.

\begin{cor}
\label{cor:main-mod-forms}
Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
associated to $\Gamma \backslash \BH$ with signature $\sigma
= (g; e_1, \ldots, e_r; \delta)$.

If $M_k(\Gamma) = 0$ for all odd $k$, then the ring of modular
forms $M(\Gamma)$ is generated as a $\BC$-algebra by elements of
degree at most $3 \cdot \max(3, e_1, \ldots, e_r)$ with relations
generated in degrees at most $6 \cdot \max(3, e_1,\ldots, e_r)$.

If there is some odd $k$ for which $M_k(\Gamma) \neq 0$, then the
ring of modular forms $M(\Gamma)$ is generated as a $\BC$-algebra
by elements of degree at most $\max(5, e_1, \ldots, e_r)$ with
relations generated in degree at most $2 \cdot \max(5, e_1, \ldots, 
e_r)$ so long as $\sigma$ does not lie in a finite list of
exceptional cases which are listed and described in Table
~\ref{table:g-1-exceptional} for signatures with $g = 1$ and in
Table ~\ref{table:g-0-exceptional} for signatures with $g = 0$.
\end{cor}

@@

@@

\begin{rem}
Note that the ordering of the variables matters in Equation
~\ref{eqn:grevlex-tie}.
\end{rem}

@@

We can directly see that the relations are given in degrees $10$
and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{5, 1}^2 + a_2 x_{7, 2} x_{3, 1} + a_3 x_{7, 1} x_{3, 1} = 
	0 &\text{ in degree $10$} \\
	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
\end{align*}

\noindent
and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
have that
\[
	a_2 x_{7, 2} x_{3, 1} = -a_3 x_{7, 1} x_{3, 1}
\]

\noindent
However, $x_{7, 2} x_{3, 1}$ has pole orders $(3, 3, 4)$ and
$x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ so their
coefficients must be zero for this equality to hold. We have a
similar pole order consideration in forcing $b_1$ to be nonzero.

Let $I$ be the ideal generated by these relations in
$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grevlex with
$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
ideal of $I$ is
\[
	\initial(I) = \langle x_{7, 2}^2, x_{5, 1}^2 \rangle
\]

@@

\begin{align*}
	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I)_d &=
	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial_\prec(I))_d \\
	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
	x_{7, 2}^2, x_{5, 1}^2 \rangle
\end{align*}

\noindent
for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{5, 1}^2
\rangle$ can be checked by looking at the $k$-basis at each degree
$d$.

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}] / I$ with
initial ideal $\initial(I)$ generated by quadratics under grlex
with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to degree $e = 7$ with relations up to
degree $2e = 14$, as desired.

@@

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l \in \BN_{\ge 0}\}
\]
and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j S_{i-j}.
\]
Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
\[
	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
\]
Then define 
\begin{equation}\label{eqn:sat-1-defining-S}
	S = \cup_{i=1}^{\infty} S_i.  
\end{equation}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

@@

{\bf Part (b):}
Let $S$ be as above in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
\[
	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
\]

@@

It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}. To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$. Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
\]
Notice that $S$ generates the ideal $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$; let $l$ be maximal such that $a_l\ne 0$.
If $i\in \{1, \ldots, n\}$, then $y_i f$ is either in $S$ or there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
and for all $r<h$ $\prod_{j=1}^r {y_j}^{b_j}\in S$, where $b_j=a_j$ when $j\ne i$ and $b_i=a_i+1$.  Choose $(\gamma_1, \ldots, \gamma_n)$ minimal (that is, so that we cannot decrease any $\gamma_j$ and have the following still satisfied) such that each $\gamma_j\le b_j$ and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S$; our recursive definition of $S$ implies that for each $1\le r< h$, we still have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.

We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).  Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).  Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above immediately gives (**).  Since for each $r<h$, $\prod_{j=1}^r y_{j}^{a_j}\in S$, we get condition (***).  Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.

Since $S$ generates $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\{y_1, \ldots, y_n\} k[y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

\ssec{Genus One Base Cases}
\label{ssec:g_1_base}
In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g = 1$.

\begin{longtable}	{| c || c | c | c |}	
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ & $1$ \\	\hline

	$\frac{3}{7} P_1$ & $\{1,5,7\}$ & $\{15\}$ & $7$ \\	\hline

	$\frac{1}{3} P_1 + \frac{1}{3} P_2$ & $\{1, 3, 3\}$ & $\{6\}$ & $5$ \\	\hline

	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$ \\	\hline

	$P - Q + \frac{1}{3} P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ & $5$ \\	\hline

@@

\ssec{Genus One Exceptional Cases}
\label{ssec:g-1-exceptional}
Let $\sx$ be a stacky curve, with $P, Q$ distinct hyperelliptic
fixed points on $X$. The following table provides a list of all
cases which are not generated in degrees $e := \max(5, e_1, \ldots,
e_r)$ with relations in degrees $2e$, as described in Theorem
~\ref{thm:g-1-main}.

\begin{longtable}	{| c || c | c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations & $e$ \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ & $1$\\	\hline

	$P - Q + \frac{1}{3} P_1$ & $\{2, 3, 7\}$ & $\{14\}$ & $5$ \\	\hline

	$P - Q + \frac{2}{5} P_1$ & $\{2, 3, 5\}$ & $\{12\}$ & $5$\\	\hline

	$\frac{1}{3} P_1$ & $\{1, 6, 9\}$ & $\{18\}$ & $5$ \\	\hline

	$\frac{2}{5} P_1$ & $\{1, 5, 8\}$ & $\{16\}$ & $5$ \\	\hline

	$\frac{3}{7} P_1$ & $\{1, 5, 7\}$ & $\{15\}$ & $7$ \\	\hline

@@

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
0$, the proof is a rather involved induction using Lemma
~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
remainder of this section is dedicated to characterizing the
saturations (Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g-0-main}.

@@

\begin{longtable}
	{| c | c || c |}
	\hline
	Signature $\sigma$ & Condition & Saturation \\
	\hline
	\hline

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\hline
	Case & Signature $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
	\hline
	\hline

@@

\begin{longtable}
	{| c || c | c | c |}
	\hline
	Signature $\sigma$ & Generator Degrees & Degrees of Relations & $e$ \\
	\hline
	\hline

>>>>

\todo{I changed the following to incorporate the no odd weight case. Is it ok?}

The main theorem of this paper, Theorem ~\ref{thm:main}, combined with a result of Voight and
Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky}, together with Voight and Zureick-Brown ~\cite[Theorem 9.3.1]{vzb:stacky} and ~\cite[9.3.1]{vzb:stacky} provide the following application
to modular forms. Note that the result from Voight and
Zureick-Brown ~\cite[Lemma 10.2.1]{vzb:stacky} follows almost immediately from the classical work of Kodaira--Spencer
\cite{kodaira-spencer:deformations}.

\begin{cor}
\label{cor:main-mod-forms}
Let $\Gamma$ be a Fuchsian group and $\sx$ the stacky curve
associated to $\Gamma \backslash \BH$ with signature $(g; e_1,
\ldots, e_r; \delta)$. 
If $M_k(\Gamma) = 0$ for all odd $k$, then $M(\Gamma)$ is generated in degree at most $3 \cdot\max(3,e_1,\ldots, e_r)$ with relations in degree at most $6 \cdot \max(3,e_1,\ldots, e_r)$.
If there is some odd $k$ for which $M_k(\Gamma) \neq 0,$ then, the ring of modular forms
$M(\Gamma)$ is
generated as a $\BC$-algebra by elements of degree at most $e = \max
 (5, e_1, \ldots , e_r)$ with relations in degree at most $2e,$ so long
as $\sigma$ does not lie in a finite list of exceptional cases, as
listed in Table ~\ref{table:g-1-exceptional} for signatures with $g
= 1$ and Table ~\ref{table:g-0-exceptional} for signatures with $g =
0$.
\end{cor}

@@

\begin{defn}
\label{defn:grlex}
The {\bf graded lexicographic} order, or {\bf grlex} $\prec_{\text{grlex}}$ on a polynomial ring $k[x_{1}, \ldots,
x_{n}]$ with $\deg x_i = d_i$ is defined as follows.
If $\alpha := \prod_{i = 1}^{n} x_{i}
^{f_i}$ and $\beta := \prod_{i = 1}^{n} x_{i}^{f_i'}$ are
monomials in $k[x_{1}$, $\ldots$, $x_{n}]$, then $\alpha
\succ_{\text{grlex}} \beta$ if either $\alpha$ has larger degree:

\begin{equation}
	\deg \alpha := \sum_{i = 1}^{n} d_i f_i  > \sum_{i = 1}^{n} d_i f_i' =: \deg \beta
\end{equation}
or
\begin{equation}
\label{eqn:grlex-tie}
	\deg \alpha = \deg \beta \text{ and }
	f_i - f_i' > 0 \text{ for the smallest } i \text{ such that } f_i \neq f_i'.
\end{equation}
\end{defn}

@@

\begin{rem}
Note that the ordering of the variables matters in both
Equation ~\ref{eqn:grlex-tie} and Equation ~\ref{eqn:grevlex-tie}.
\end{rem}

@@

We can directly see that the relations are given in degrees $10$
and $14$. In particular, we have relations
\begin{align*}
	&a_1 x_{7, 2} x_{3, 1} + a_2 x_{7, 1} x_{3, 1} + a_3 x_{5, 1}^2 = 
	0 &\text{ in degree $10$} \\
	&b_1 x_{7, 2}^2 + b_2 x_{7, 2} x_{7, 1} + b_3 x_{7, 1}^2
	+ b_4 x_{5, 1} x_{3, 1}^3 = 0  &\text{ in degree $14$}
\end{align*}

\noindent
and note that $a_1$ and $b_1$ are both nonzero. If $a_1 = 0$, then we
have that
\[
	a_2 x_{7, 1} x_{3, 1} = -a_3 x_{5, 1}^2
\]

\noindent
However, $x_{7, 1} x_{3, 1}$ has pole orders $(3, 4, 3)$ and
$x_{5, 1}^2$ has pole orders $(2, 4, 4)$ so their
coefficients must be zero for this equality to hold. We have a
similar pole order consideration in forcing $b_1$ to be nonzero.

Let $I$ be the ideal generated by these relations in
$k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]$. Under grlex with
$x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$, the initial
ideal of $I$ is
\[
	\initial(I) = \langle x_{7, 2}^2, x_{7, 2} x_{3, 1} \rangle
\]

@@

\begin{align*}
	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / I)_d &=
	\dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}])	/ \initial_\prec(I))_d \\
	&= \dim_k (k[x_{7, 2}, x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle
	x_{7, 2}^2, x_{3, 1} x_{7, 2} \rangle
\end{align*}

\noindent
for all $d \geq 0$. But the fact $\dim_k (R')_d = \dim_k (k[x_{7, 2},
x_{7, 1}, x_{5, 1}, x_{3, 1}]) / \langle x_{7, 2}^2, x_{3, 1} x_{7, 2}
\rangle$ can be checked by looking at the $k$-basis at each degree
$d$.

Therefore, the canonical ring $R'$ has presentation $R' =
k[x_{7, 2}^2, x_{3, 1} x_{7, 2}] / I$ with
initial ideal $\initial(I)$ generated by quadratics under grlex
with $x_{3,1} \prec x_{5,1} \prec x_{7,1} \prec x_{7,2}$.
%These quadratics must also determine minimal generators for $I$ by
%Lemma ~\ref{lem:minimal_quadratic}.
Thus, $R'$ is generated up to degree $e = 7$ with relations up to
degree $2e = 14$, as desired.

@@

Using Equation ~\ref{eqn:c-from-lower-terms}, we recursively define a $k$-basis for $R_\halfcan$ over $R_{\halfcan'}$. Define 
\[
	S_0 = \{u^l : l \in \BN_{\ge 0}\}
\]
and for each $i \in \BN$, suppose $c_j$ is the maximal element among of $c_1, \ldots c_n$ such that $c_j \le i.$ Note that such a $c_j$ exists because $1=c_1\le i.$ Define
\[
	S_i = y_j \cdot S_{i-j}.
\]
Since each $y_j$ has pole order $c_j$, this recursive construction ensures that 
\[
	z\in S_i \implies -\ord_P^{\halfcan'}(z)=i.
\]
Then define 
\begin{equation}\label{eqn:sat-1-defining-S}
	S = \cup_{i=1}^{\infty} S_i.  
\end{equation}
Note that $S_0$ is not part of this union and in fact $S\cap S_0 = \emptyset$ by pole order considerations.

@@

{\bf Part (b):}
Let $S$ be as defined in Equation \ref{eqn:sat-1-defining-S}, define $U_i$ and $V$ as in the lemma's statement, and set
\[
	T = \left(\bigcup_{i=1}^{n-1} U_i \right) \cup V.
\]

@@

It only remains to check condition (3) of Lemma ~\ref{lem:relations_from_generators_induction}. To do this, suppose $f\in k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ is a monomial not contained in $k[u, x_1, \ldots, x_m]$, meaning there is some $j$ such that $y_j|f$.  Further suppose $f\not\in \langle V \rangle$, meaning that for each $i\in \{1, \ldots m\}$, $x_iy_j \nmid f$. Since $y_j \mid f$ but $x_iy_j \nmid f$, we obtain $x_i\nmid f$.  Therefore, $f\in k[u, y_1, \ldots, y_n]$.  We note that $S$ generates $y_j \cdot (k[u,y_1, \ldots, y_n])$ as a $k$-algebra.  That is, all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\[
	k[u, x_1, \ldots, x_m] \cup V \cup \left(\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]\right). 
\]
Notice that $S$ generates the ideal $(y_1, \ldots, y_n)$ considered as an ideal of the subring $k[u, y_1, \ldots, y_n]$.  If $f\in S$, then $f=u^b \prod_{j=1}^n {y_j}^{a_j}$. Let $l$ be maximal such that $a_l\ne 0$.
Fix $i \in \{1, \ldots, n\}$. If $y_i \cdot f \notin S$, define
$$
b_j = \begin{cases}
	a_j &\text{ if } j \neq i\\
	a_j + 1 &\text{ if } j=i.
\end{cases}$$

\noindent
Then, there is some $h \in \BN$ such that $i\le h\le \max(i,l)$ satisfying $\prod_{j=1}^h y_j^{b_j}\not\in S$, 
and for all $r<h$ we have $\prod_{j=1}^r {y_j}^{b_j}\in S$.  
Choose some tuple $(\gamma_1, \ldots, \gamma_n)$ which is minimal, in the sense that we cannot decrease any $\gamma_j$ 
and have the following still satisfied: each $\gamma_j\le b_j$ 
and $\prod_{j=1}^h {y_j}^{\gamma_j}\not\in S.$ Our recursive definition of 
$S$ and the fact that $\prod_{j=1}^r {y_j}^{b_j}\in S$ implies that for each $1\le r< h$, we have $\prod_{j=1}^r {y_j}^{\gamma_j}\in S$.

We now check that $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$, by checking conditions (*), (**), and (***).  Since $\prod_{j=1}^{h-1} y_j^{b_j}\in S$ but $\prod_{j=1}^h y_j^{b_j}\not\in S$, $c_h$ must not be maximal (among pole orders of the $y_i$'s) such that $c_h \le \sum_{j=1}^h b_jc_j$ (otherwise, it would be in $S$), which means $c_{h+1}\le \sum_{j=1}^h b_jc_j$, giving us condition (*).  Our choice of $(\gamma_1, \ldots, \gamma_n)$ to be minimal above implies (**).  Since for each $r<h$, we have $\prod_{j=1}^r y_{j}^{a_j}\in S$, condition (***) holds.  Thus $\prod_{j=1}^h y_j^{\gamma_j}\in U_{\sum_{j=1}^h b_j c_j}$.

\todo{how to avoid polynomials hangining over lines like this, ask david} Since the ideal in $k[u, y_1,\ldots, y_n]$ generated by is $S$ is $(y_1, \ldots, y_n) \cdot k[u, y_1, \ldots, y_n]$ and $\bigcup_{i=1}^{n-1} U_i$ generates every monomial in $\cup_{i=1}^n y_i \cdot k[u, y_1, \ldots, y_n]-S$, we have shown that all monomials of $k[u, x_1, \ldots, x_m, y_1, \ldots, y_n]$ are contained in
\begin{align*}
				& k[u, x_1, \ldots, x_m] \cup \langle V \rangle \cup S \cup \left\langle \bigcup_{i=1}^{n-1} U_i \right\rangle \\
	\subseteq \; 	& S \cup \langle T\rangle \cup \initial(I') k[u, x_1, \ldots, x_m, y_1, \ldots, y_n] \; \cup \; k[u, x_1, \ldots, x_m].
\end{align*}
This shows condition (3) of Lemma ~\ref{lem:relations_from_generators_induction} holds.  Thus, the conditions of 
Lemma ~\ref{lem:relations_from_generators_induction} are met. Finally, Lemma ~\ref{lem:relations_from_generators_induction} implies part (b).  \todo{Peter: Checking that all the conditions of Lemma \ref{lem:relations_from_generators_induction}(2) are met takes a lot of space and clutter.  On the other hand, it is somewhat important.  Should it be included?}

@@

\ssec{Genus One Base Cases}
\label{ssec:g_1_base}
In this subsection we set up the base cases needed for our inductive approach, of proving Theorem ~\ref{thm:main} in the case $g=1$.

\begin{longtable}	{| c || c | c |}	
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$0$ & $\{1\}$ & $\emptyset$ \\	\hline

	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline

	$\frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{1, 3, 3\}$ & $\{6\}$ \\	\hline

	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

	$P - Q + \frac{1}{3}P_1 + \frac{1}{3}P_2$ & $\{2, 3, 3, 4\}$ & $\{6,8\}$ \\	\hline

@@

\ssec{Genus One Exceptional Cases}
\label{ssec:g-1-exceptional}
Let $\sx$ be a stacky curve, with Let $P,Q$ distinct hyperelliptic fixed points on $X$. The following table provides a list of all cases which are not generated in degrees $e=\max(5,e_1,\ldots, e_r)$ with relations in degrees $2e$, as described in Theorem ~\ref{thm:g-1-main}.

\begin{longtable}	{| c || c | c |}
	\hline
	L' & Generator Degrees & Degrees of Minimal Relations \\
	\hline
	\hline
	$P - Q$ & $\{2\}$ & $\emptyset$ \\	\hline

	$P - Q + \frac{1}{3}P_1$ & $\{2,3,7\}$ & $\{14\}$ \\	\hline

	$P - Q + \frac{2}{5}P_1$ & $\{2,3,5\}$ & $\{12\}$ \\	\hline

	$\frac{1}{3}P_1$ & $\{1,6,9\}$ & $\{18\}$ \\	\hline

	$\frac{2}{5}P_1$ & $\{1,5,8\}$ & $\{16\}$ \\	\hline

	$\frac{3}{7}P_1$ & $\{1,5,7\}$ & $\{15\}$ \\	\hline

@@

There are two main cases: when $\delta \geq 2$ and when $\delta = 0$,
where we are implicitly appealing to Remark ~\ref{rem:delta-not-1}.
In the first case, $\deg \lfloor \halfcan \rfloor \geq 0$ so the
result directly follows from Lemma ~\ref{lem:sat-1}. When $\delta =
0$, the proof is a rather involved induction using Lemma
~\ref{lem:sat-3} and Lemma ~\ref{lem:raise-stacky-order}. The
remainder of this section is dedicated to characterizing the
saturations ( Subsection ~\ref{ssec:g_0_saturation}), inductive
base cases ( Subsection ~\ref{ssec:g_0_base}), and exceptional
cases (Subsection ~\ref{ssec:g-0-exceptional}) when $\delta = 0$
before proving the main theorem in full for all $\delta$ in
Subsection ~\ref{ssec:g-0-main}.

@@

\begin{longtable}
	{| c | c || c |}
	\hline
	Signature & Condition & Saturation \\
	\hline
	\hline

@@

\begin{longtable}
	{| c | c | c || c | c |}
	\hline
	Case & $\sigma$ & $J$ & $\deg \lfloor e_i L \rfloor$ &
	$\max_{d \geq 0} \#S_{(\sigma, J)}(i)$ \\
	\hline
	\hline

@@

\begin{longtable}
	{| c || c | c | c |}
	\hline
	Signature & Generator Degrees & Degrees of Relations & $e$ \\
	\hline
	\hline
